### 2017-04-17 paper/evaluation.tex
RQ6 - preliminar list

\begin{figure}[h!]
\centering
\resizebox{.48\textwidth}{!}{%
\begin{tabular}{lrrrrrr}
\toprule
\emph{Subject} & \Seq{} & \SeqClassParMeth{} & \ParClassSeqMeth{} & \ParClassParMeth{} & \ForkSeq{} & \ForkParMeth{}\\%
\midrule%
BounceStorage \textbf{Chaos} HTTP Proxy  & 1.47m & 1.00x & 1.00x & 1.00x & 1.00x & 1.00x\\%
\bottomrule%
\end{tabular}}
\caption{\Fix{Tabela de eficiencia}}
\label{tab:rq6-efficiency}
\end{figure}

@@

\begin{figure}[h!]
\centering
\resizebox{.48\textwidth}{!}{%
\begin{tabular}{lcrrrrr}
\toprule
\emph{Subject} & \emph{\# of tests} & \SeqClassParMeth{} & \ParClassSeqMeth{} & \ParClassParMeth{} & \ForkSeq{} & \ForkParMeth{}\\%
\midrule%
BounceStorage \textbf{Chaos} HTTP Proxy  & 8765 & 10\% & 10\% & 10\% & 10\% & 10\%\\%
\bottomrule%
\end{tabular}}
\caption{\Fix{Tabela de flakiness}}
\label{tab:rq6-flaky}
\end{figure}

>>>>

\begin{figure}[h!]
\centering
\resizebox{.48\textwidth}{!}{%
\begin{tabular}{lrrrrrr}
\toprule
\emph{Subject} & \Seq{} & \SeqClassParMeth{} & \ParClassSeqMeth{} & \ParClassParMeth{} & \ForkSeq{} & \ForkParMeth{}\\%
\midrule%
%% BounceStorage \textbf{Chaos} HTTP Proxy  & 1.47m & 1.00x & 1.00x & 1.00x & 1.00x & 1.00x\\%
Snazy OHC & - & - & - & - & - & -\\%
RoaringBitmap & - & - & - & - & - & -\\%
Linkedin Pinot & - & - & - & - & - & -\\%
Jenkinsci Github-Plugin & - & - & - & - & - & -\\%
Geotools & - & - & - & - & - & -\\%
Kite-SDK Kite & - & - & - & - & - & -\\%
Apache Giraph & - & - & - & - & - & -\\%
Openmrs Core & - & - & - & - & - & -\\%
Jenkinsci Docker-Workflow-plugin & - & - & - & - & - & -\\%
Apache Eagle & - & - & - & - & - & -\\%
\bottomrule%
\end{tabular}}
\caption{\Fix{Tabela de eficiencia}}
\label{tab:rq6-efficiency}
\end{figure}

@@

\begin{figure}[h!]
\centering
\resizebox{.48\textwidth}{!}{%
\begin{tabular}{lcrrrrr}
\toprule
\emph{Subject} & \emph{\# of tests} & \SeqClassParMeth{} & \ParClassSeqMeth{} & \ParClassParMeth{} & \ForkSeq{} & \ForkParMeth{}\\%
\midrule%
%% BounceStorage \textbf{Chaos} HTTP Proxy  & 8765 & 10\% & 10\% & 10\% & 10\% & 10\%\\%
Snazy OHC & - & - & - & - & - & -\\%
RoaringBitmap & - & - & - & - & -\\%
Linkedin Pinot & - & - & - & - & -\\%
Jenkinsci Github-Plugin & - & - & - & - & -\\%
Geotools & - & - & - & - & -\\%
Kite-SDK Kite & - & - & - & - & -\\%
Apache Giraph & - & - & - & - & -\\%
Openmrs Core & - & - & - & - & -\\%
Jenkinsci Docker-Workflow-plugin & - & - & - & - & -\\%
Apache Eagle & - & - & - & - & -\\%
\bottomrule%
\end{tabular}}
\caption{\Fix{Tabela de flakiness}}
\label{tab:rq6-flaky}
\end{figure}
